### 2016-04-23 manuscript-body.tex
fix curly quotes; fix a couple of typos

\hypertarget{sandiwches-code}{\label{sandwiches-code}}
\begin{Shaded}
\begin{Highlighting}[numbers=left,,]
\NormalTok{Cheese[] cheeses = }\KeywordTok{new} \NormalTok{Cheese[}\DecValTok{4}\NormalTok{];}
\NormalTok{Meat[] meats = }\KeywordTok{new} \NormalTok{Meat[}\DecValTok{2}\NormalTok{];}
\NormalTok{Turkey turkey;}
\NormalTok{Ham ham;}
\NormalTok{RoastBeef roastBeef;}
\DataTypeTok{boolean} \NormalTok{lettuce = }\KeywordTok{true}\NormalTok{;}
\DataTypeTok{boolean} \NormalTok{tomato = }\KeywordTok{true}\NormalTok{;}
\NormalTok{SauceType sauceType = }\KeywordTok{new} \FunctionTok{SauceType}\NormalTok{();}
\DataTypeTok{int} \NormalTok{numMeat;}
\DataTypeTok{int} \NormalTok{numCheese;}
\end{Highlighting}
\end{Shaded}

@@

In our kinematics debugging example, cognition gets distributed across time and space (1) by creating a visual trace of the animated object's position (a persistent trail of dots). And, it is this act of dot-tracing that lets a programmer invokve spatial-adjacency perception and conceptual kinematics knowledge (how positions uniformly sampled in time can reflect constant velocity vs. acceleration) that wouldn't seem applicable if the reassignment statement were stripped of its context.

@@

 If we view the assignment statement as proposing
something about the motion of an object---as, for example, when sense-making in science and engineering students can view equations as ``saying something'' about how a system behaves[blinded]---a
field of knowledge and concomitant techniques from physics become
available to me to think with. But, if we focus only on the
semantic-level equivalence of statements 1 through 5, there would be no
obvious reason for me to access what we know about physics in order to
reason about the code.

@@

\begin{quote}
  In explaining the phenomenon, Erin focuses on the role played by the air located inside the juice box. She describes the air inside as actively pushing out on all sides of the box holding them out and flat. When that air is removed from the box (by sucking it out through the straw), there is no longer anything pushing from the inside to hold the box out, so the sides cave in. We call this description of the phenomenon the “inside-pusher” model because of its focus on what happens inside the box. \cite{russ_making_2008}
\end{quote}

>>>>

\hypertarget{sandwiches-code}{\label{sandwiches-code}}
\begin{Shaded}
\begin{Highlighting}[numbers=left,,]
\NormalTok{Cheese[] cheeses = }\KeywordTok{new} \NormalTok{Cheese[}\DecValTok{4}\NormalTok{];}
\NormalTok{Meat[] meats = }\KeywordTok{new} \NormalTok{Meat[}\DecValTok{2}\NormalTok{];}
\NormalTok{Turkey turkey;}
\NormalTok{Ham ham;}
\NormalTok{RoastBeef roastBeef;}
\DataTypeTok{boolean} \NormalTok{lettuce = }\KeywordTok{true}\NormalTok{;}
\DataTypeTok{boolean} \NormalTok{tomato = }\KeywordTok{true}\NormalTok{;}
\NormalTok{SauceType sauceType = }\KeywordTok{new} \FunctionTok{SauceType}\NormalTok{();}
\DataTypeTok{int} \NormalTok{numMeat;}
\DataTypeTok{int} \NormalTok{numCheese;}
\end{Highlighting}
\end{Shaded}

@@

In our kinematics debugging example, cognition gets distributed across time and space (1) by creating a visual trace of the animated object's position (a persistent trail of dots). And, it is this act of dot-tracing that lets a programmer invoke spatial-adjacency perception and conceptual kinematics knowledge (how positions uniformly sampled in time can reflect constant velocity vs. acceleration) that wouldn't seem applicable if the reassignment statement were stripped of its context.

@@

 If we view the assignment statement as proposing
something about the motion of an object---as, for example, when sense-making in science and engineering students can view equations as ``saying something'' about how a system behaves [blinded]---a
field of knowledge and concomitant techniques from physics become
available to me to think with. But, if we focus only on the
semantic-level equivalence of statements 1 through 5, there would be no
obvious reason for me to access what we know about physics in order to
reason about the code.

@@

\begin{quote}
  In explaining the phenomenon, Erin focuses on the role played by the air located inside the juice box. She describes the air inside as actively pushing out on all sides of the box holding them out and flat. When that air is removed from the box (by sucking it out through the straw), there is no longer anything pushing from the inside to hold the box out, so the sides cave in. We call this description of the phenomenon the "inside-pusher" model because of its focus on what happens inside the box. \cite{russ_making_2008}
\end{quote}
